Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-04-30 paper/paper.tex
qb test
add citations 6 & 7 to related works

\section{Related Works}
While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
studies that attempt to determine the answer. The other studies attempted to search for this answer by
focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, 
or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}. Similar to~\cite{kiss2021effect},~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''. A different study done in 2010 again found similar results of music both being a hindrance and benefit~\cite{AudioDistractionsAshley}. According to~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality.

@@

The study done through~\cite{kiss2021effect} saw opposite results as to~\cite{Gonzalez_Aiello_2019}. The music or background noise ``enhanced'' the reaction time and performance of the tasks that are given to be completed. The results from~\cite{mathew2022inherently} were split. The music was a detriment for logic puzzles in the user's accuracy but aided in the efficiency of a writing task.

>>>>

\section{Related Works}
While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
studies that attempt to determine the answer. The other studies attempted to search for this answer by
focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, 
or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}. Similar to~\cite{kiss2021effect},~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''. A different study done in 2010 again found similar results of music both being a hindrance and benefit~\cite{AudioDistractionsAshley}. According to~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality.  The research done by Komlao found that music or background music was again based on an individual's personality but that music, even music that the participants were familiar with, were a distraction and ``was found to negatively impact task performace'' overall~\cite{komlao2018variations}. This was contrary to the previous studies found by Komlao where the ``music could help increase productivity for simple, monotonouse tasks''~\cite{komlao2018variations}.

@@

The study done through~\cite{kiss2021effect} saw opposite results as to~\cite{Gonzalez_Aiello_2019}. The music or background noise ``enhanced'' the reaction time and performance of the tasks that are given to be completed. The results from~\cite{mathew2022inherently} were split. The music was a detriment for logic puzzles in the user's accuracy but aided in the efficiency of a writing task. According to Bramwell-Dicks et el, the instrumental music used in their study had better results on typists in speed and accuracy whereas music with vocals, the participants fared worse~\cite{bramwell2016can}.
